---
title: "p8105_hw6_ak4123"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
set.seed(1)
```

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. 
``` {r}
homicides = read.csv("./data/homicide-data.csv")

homicides = homicides %>% 
  mutate(city_state = paste(city, state, sep = ", "),
         resolution = as.numeric(disposition == "Closed by arrest"),
         victim_race_binary = case_when(
           victim_race == "Asian" ~ "Non-White",
           victim_race == "Black" ~ "Non-White",
           victim_race == "Hispanic" ~ "Non-White",
           victim_race == "Other" ~ "Non-White",
           victim_race == "Unknown" ~ "Non-White",
           victim_race == "White" ~ "White"
         ),
         victim_race = factor(victim_race_binary, levels = c("White", "Non-White")),
         victim_age = as.numeric(as.character(victim_age))
  ) %>% 
  filter(city_state != "Dallas, TX" & city_state != "Phoenix, AZ" & city_state != "Kansas City, MO" & city_state != "Tulsa, AL")
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.

```{r} 
logistic = 
  homicides %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(resolution ~ victim_age + victim_sex + victim_race, data = ., family = binomial())
logistic %>% 
  broom::tidy() %>% 
  janitor::clean_names() %>% 
  mutate(OR = exp(estimate),
         lower_ci = exp(estimate - (1.96 * std_error)),
         upper_ci = exp(estimate + (1.96 * std_error))) %>%
  filter(term == "victim_raceNon-White") %>% 
  select(OR, lower_ci, upper_ci) %>% 
  knitr::kable()
```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}
logistic =
  homicides %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(resolution ~ victim_age + victim_sex + victim_race, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data)

logistic = logistic %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
  mutate(OR = exp(estimate),
         lower_ci = exp(estimate - (1.96 * std_error)),
         upper_ci = exp(estimate + (1.96 * std_error))) %>% 
  filter(term == "victim_raceNon-White") %>%
  select(city_state, OR, lower_ci, upper_ci) 
  
logistic %>% 
  knitr::kable()
```

```{r}
nest_glm_res =
  homicides %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(resolution ~ victim_age + victim_sex + victim_race, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data)

glm_homicides = nest_glm_res %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
  mutate(OR = exp(estimate),
         lower_ci = exp(estimate - (1.96 * std_error)),
         upper_ci = exp(estimate + (1.96 * std_error))
  ) %>% 
  filter(term == "victim_raceNon-White") %>%
  select(city_state, OR, lower_ci, upper_ci) 
  
glm_homicides %>% 
  knitr::kable()
```

```{r}
glm_homicides %>% 
  mutate(city_state = forcats::fct_inorder(city_state)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci)) +
  labs(
    x = "City, State",
    y = "ORs",
    title = "ORs and 95% CIs for Solved Cases Comparing Non-whites to Whites"
  ) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 5)) 
```

##QUESTION 2
Load and clean the data for regression analysis:
```{r}
birthweight = read.csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~ "Male",
      babysex == 2 ~ "Female"),
    babysex = fct_relevel(babysex, "Male"),
    frace = case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other",
      frace == 9 ~ "Unknown"),
    frace = fct_relevel(frace, "White"),
    malform = case_when(
      malform == 0 ~ "Absent",
      malform == 1 ~ "Present"),
    malform = fct_relevel(malform, "Absent"),
    mrace = case_when(
      mrace == 1 ~ "White",
      mrace == 2 ~ "Black",
      mrace == 3 ~ "Asian",
      mrace == 4 ~ "Puerto Rican",
      mrace == 8 ~ "Other"),
    mrace = fct_relevel(mrace, "White")
  )
missing_data = sum(is.na(birthweight))
```

Propose a regression model for birthweight. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
```{r}
model_bwt = 
  lm(bwt ~ delwt+fincome+menarche+mheight+momage+mrace+ pnumlbw+pnumsga+ppbmi+ppwt, data = birthweight)
```
This model is based on maternal factors that could affect birthweight. The plot of the model residuals against fitted values is below.
```{r}
birthweight %>% 
  modelr::add_residuals(model_bwt) %>% 
  modelr::add_predictions(model_bwt) %>% 
  ggplot(aes(x = pred, y = resid)) +
    geom_point() +
  labs(
    x = "Risiduals",
    y = "Prediction",
    title = "Model Residuals Against Fitted Values")
```

Compare your model to two others:
One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
model_A = lm(bwt ~ blength + gaweeks, data = birthweight)
model_B = lm(bwt ~ bhead + blength + babysex + bhead*babysex + blength+babysex + bhead*blength*babysex + bhead*blength, data = birthweight)
```
Make this comparison in terms of the cross-validated prediction error
```{r}
cv_bwt = 
  crossv_mc(birthweight, 100)
cv_bwt = 
  cv_bwt %>% 
  mutate(model_bwt = map(train, ~lm(bwt ~ delwt + gaweeks + ppwt + smoken, data = birthweight)),
         model_A = map(train, ~lm(bwt ~ blength + gaweeks, data = birthweight)),
         model_B = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*babysex + blength+babysex + bhead*blength*babysex + bhead*blength, data = birthweight))) %>% 
  mutate(rmse_bwt = map2_dbl(model_bwt, test, ~rmse(model = .x, data = .y)),
         rmse_A = map2_dbl(model_A, test, ~rmse(model = .x, data = .y)),
         rmse_B = map2_dbl(model_B, test, ~rmse(model = .x, data = .y)))
```
